DNA Methylation Hierarchical Variance Model\nPaper Figures

### 2021-07-07 Paper_Figures.Rmd
changes to paper figures script

# Fig 4B: plot gene scores and adjusted bootstrap distribution
p1 <- permed_data %>% ggplot(aes(x=score_median)) + geom_histogram(aes(y=..count..), binwidth=0.2, fill="lightgray",color = "grey50") + theme_classic() + ylab("Number of genes") + theme(aspect.ratio = 1) + scale_x_continuous(breaks = c(-2,0,2,4,6), limits = c(-3,7)) + scale_y_continuous(breaks = c(0,1000,2000,3000), limits = c(0,3000))
p2 <- permed_data %>% ggplot(aes(x=score_median_v3)) + geom_histogram(aes(y=..count..), binwidth=0.02, fill="lightgray", color="grey50") + xlim(c(0,1)) + theme_classic() + ylab("Number of genes") + theme(aspect.ratio = 1)
p_genes <- ggarrange(p1,p2,nrows=1,ncol=2)
ggsave("gene_scores_median.svg", plot=p1)
ggsave("gene_scores_bootstrap.svg", plot=p2)
```

>>>>

# Fig 4B: plot gene scores and adjusted bootstrap distribution
p1 <- permed_data %>% ggplot(aes(x=score_median)) + geom_histogram(aes(y=..count..), binwidth=0.2, fill="lightgray",color = "grey50") + theme_classic() + ylab("Number of genes") + theme(aspect.ratio = 1) + scale_x_continuous(breaks = c(-2,0,2,4,6), limits = c(-3,7)) + scale_y_continuous(breaks = c(0,1000,2000,3000), limits = c(0,3000))
p2 <- permed_data %>% ggplot(aes(x=score_median_v3)) + geom_histogram(aes(y=..count..), binwidth=0.02, fill="lightgray", color="grey50") + xlim(c(0,1)) + theme_classic() + ylab("Number of genes") + theme(aspect.ratio = 1)
p_genes <- ggarrange(p1,p2,nrows=1,ncol=2)
ggsave("gene_scores_median.svg", plot=p1)
ggsave("gene_scores_bootstrap.svg", plot=p2)

# save significant bootstrapped genes as csv
sig_genes = permed_data %>% filter(score_median_v3>=0.95) %>% pull(UCSC_RefGene_Name)
write_csv(data.frame(Gene = sig_genes), file = "sig_cons_genes.csv")
# for Reactome pathway analysis at https://reactome.org/PathwayBrowser
```
